---
title: "martah_OriginalHomeworkCode_01"
author: "Marta"
date: "9/12/2021"
output: 
  html_document:
  toc: true
  toc_float: true
  theme: cosmo
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- For starters I am entirely unsure what this first chunk does to the R markdown document?? If you guys could help explain it would be greatly appreciated 

# Module 4  

## Challenge 1  

``` {r charvector}
v1<- c("Stately, ", "plump ", "Buck ", "Mulligan ", "came ", "from ", "the ", "stairhead, ", "bearing ", "a ", "bowl ", "of ", "lather ", "on ", "which ", "a ", "mirror ", "and ", "a ", "razor ", "lay ", "crossed.")  
v1
v1[seq(from = 1, to = 22, by = 3)]
```
- sooooo I incorrectly ran stringr- that's why the code is typed out like that, and so I think in stringr it would actually be...
``` {r stringr}
library(stringr)
v1<- c("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.")
str_split(v1, boundary("word"))
```
- I'm still unsure if that is the best way to do it??? I'm also unsure how to the sequence this

## Challenge 2  

``` {r setup2}
#setup
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```
``` {r columnelements}
x<-c(m[, 2], m[, 3], m[,6])
x
  #gives the elements from columns 2, 3, and 6
  #unsure if this is suppose to be segmented?
```
```{r xassign}
x<-c(m[6,], m[8,])   
x
  #assigns variable x the elements from rows 6 and 8
```
```{r xassign2}
x<-c(m[2, 2]:m[6, 9])  
x
  #assigns the elements from (row 2, column 2) to (row 6, column 9) to the variable x
```

## Challenge 3

```{r matrixsetup}
a<-array(c(400:1), dim = c(5, 5, 4, 4))  
a

a[1, 1, 1, 2]  

a[2, 3, 2, ]

a[1:5, 1:5, 3, 3]  
```

## Challenge 4

```{r taxonomy}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
  Tarsioidea<- c("Tarsiidae")
  Catarrhini<- c("Cercopithecidae", "Hylobatidae", "Hominidae")
  Platyrrhini<- c("Cebidae", "Atelidae", "Pitheciidae")
  Anthropoidea<- list(Catarrhini, Platyrrhini)
    names(Anthropoidea)<- list("Catarrhini", "Platyrrhini")
  Haplorhini<- list(Anthropoidea, Tarsioidea)
    names(Haplorhini)<- list("Anthropoidea", "Tarsioidea")
Haplorhini
  Primates<- list(Haplorhini, Strepsirhini)
    names(Primates)<- list("Haplorhini", "Strepsirhini")
Primates
```

## Challenge 5

``` {r lastmatrix}
m3<-matrix(c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), ncol=5, nrow=3, byrow=TRUE)
m3

df<-data.frame(m3)
df

df[, c(2)]<-as.logical(df[, c(2)]) #idk why the values equal true or false?
df[, c(3)]<-as.factor(df[, c(3)])
str(df)
```